\documentclass[10pt,a4paper,sans]{moderncv}
\usepackage{xcolor}
\moderncvstyle{banking}
\definecolor{myorange}{RGB}{255,133,22}
\moderncvcolor{orange}
\nopagenumbers{}
\renewcommand{\section}[1]{\vspace{2.5ex}\textcolor{myorange}{\MakeUppercase{#1}}\par\nobreak\vspace{1ex}}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry} \usepackage{import} \usepackage{multicol}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\renewcommand*{\namefont}{\fontsize{30}{30}\mdseries\upshape\color{myorange}}
\vspace*{-1.0cm}
\name{Jeff}{Calderon}
\newcommand*{\customcventry}[7][1.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-1.2cm}
\begin{center}\textbf{ Data Scientist and Business Specialist}\end{center}
\begin{center}
\begin{tabular}{ c c c c }
\faMobile\enspace 916.712.8396  \hspace{0.1 cm}& 
\faLinkedin\enspace \href{https://www.linkedin.com/your-linkedin-profile}{/jeffdcaleron} & \hspace{0.1 cm} 
\faEnvelope\enspace kjkjk@gmail.com \hspace{0.1 cm} & 
\faHome\enspace Somewhere, WA\\
\end{tabular}
\\
\end{center}
\vspace*{-3mm}

% SUMMARY -------------------------------
\section{Summary}
{ Skilled and innovative computing professional with extensive experience in crafting custom software solution to uncover novel insights, spur data-driven 
decision making, and creating powerful visuals to formulate game-changing business decisions and workflow initiatives. Detail oriented 
with dedication to precision and integrity. An efficient manager with military leadership training. Results oriented with business acumen and economics education. 
A self-starter and skilled communicator with a persevering spirit to tackle the most daunting challenges with contagious optimism.
}

\section{Skills and Technologies}
{Strong knowledge of, statistics, Python spreadsheets, automation, project management, C++, data analytics techniques and tools.
Experienced in Network Security, data management, Leadership, Analytical thinking with a growth mindset.
Solid understanding of Power BI, Excel macros, google suite and Windows/Linux/PowerShell scripting.
Excellent communication and collaboration skills. Secret Security Clearance holder.
Ability to learn quickly and adapt to new technologies.
}

% PROFESSIONAL EXPERIENCE-------------------------------
\section{PROFESSIONAL EXPERIENCE}
\customcventry{12/2019 ‐ 05/2023}{{\color{blue}\href{https://www.omao.noaa.gov/noaa-corps}{(NOAA)}}}{Operations Manager of Marine Operations Center}{Newport, OR}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Sought data driven process-improvements with cross functional teams. Presented to region directors initiates to increase efficiency and worker retention.
\item Developed metric tracking tools and led status briefing to fleet leadership for 13 oceanographic research vessels.
\item Provided in-house software and project management support to Regional Director for shore-side support of oceanographic research vessels. Used Python, APIs databases and Smartsheet Project Management software to maintain visibility of research vessel vital statistics.
\item Managed databases, security and infrastructure, project management software, dashboard creation and metric tracking. 
\item Created and monitored Government Official Travel database and user interface. Managed data ingestion architecture; collection, storage, querying and visualizations via 
custom status tracking portal. Spearheaded a variety of workflow initiatives using automation.
\end{itemize}}}
%\hspace{0.3 cm}

\customcventry{12/2016 ‐ 05/2019}{{\color{blue}\href{https://www.omao.noaa.gov/noaa-corps}{(NOAA Commissioned Officer Corps)}}}{Hydrographer}{Ketchikan, Ak}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Composed detailed analyses and descriptive reports from sonar data and goespactial data processing tools to generate electronic navigation chart.
\item Performed Data collection, aggregation, and analysis of shipboard weather data from sensors and served as data custodian/steward.
\item Acquired, cleaned, and processed data, ETL, to create 3D rendered ocean surfaces, based on sonar, GPS, inertial motion and tidal modeling data streams.
\end{itemize}}}
%\hspace{0.3 cm}

\customcventry{01/2014 ‐ 06/2016}{{\color{blue}\href{https://www.nrl.navy.mil/}{(Naval Research Laboratory/Tech. Services Corp)}}}{Research Physicist}{Washington, DC}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Reviewed, assessed, validated, debugged and assisted in development of SWORD (Software for the Optimization of Radiation Detection) source code.
\item Developed simulations/models for detection of WMD and radiological devices in support of the Defense Threat Reduction Agency (DTRA).
\item Preformed study of personal radiation detection units for border/law enforcement; presented results from computer models and statistical analysis to validate software. 
Studies directly resulted in Domestic Nuclear Detection Office awarding 500K for continued analysis.
\item Transformed computer simulations and modeling results from technical information to digestible visualizations for non-scientist. 
\end{itemize}}}
%\hspace{0.3 cm}

\customcventry{01/2013 ‐ 04/2015}{{\color{blue}\href{https://umdphysics.umd.edu/research/research-areas/high-energy-physics.html}{(University of Maryland)}}}{Faculty Assistant Researcher}{College Park, MD}{}{
{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
\item Performed simulation studies using Hadoop and LHC computing grid 
\item Designed software and used distributed computing to analyze particle accelerator data and generate publication quality plots using C++/ROOT/LaTex Python and Linux.
\item Co-authored publications on experiments conducted at the Large Hadron Collider.
\end{itemize}}}

% CERTIFICATIONS-------------------------------
%\vspace{-0.3cm}
\section{Certifications}
%\vspace{-0.3cm}
\customcventry{Expected: NOV 2024}{\color{blue}Washington State University} {Data Analytics}{}{}{} 
\customcventry{July 2024}{\color{blue} Everett Community College } {Cybersecurity Analyst}{}{}{} 
\customcventry{July 2024}{\color{blue} CompTIA }{Network Security+}{}{}{} 
% EDUCATION-------------------------------
%\vspace{-0.3cm}
\section{Education}
\customcventry{2011-2015}{\color{blue}University of Maryland}{BS Physics}{College Park, MD}{}{}{}
\customcventry{2005-2011}{\color{blue}{University of Maryland}}{BS Social Science}{Adeplhi, MD}{}{}{}
\customcventry{2023-2024}{\color{blue}{Everett Community College }}{AAS Computer Science}{Everett, WA}{}{ president's List}{}
\newpage
\section{Professional Reference}
\vspace{-0.3cm}
{\begin{itemize}[leftmargin=0.6cm,label={\textbullet}]
    \item \textbf{Dr.  Eno} \\
          Professor of Physics, University of Maryland \\
          Email: [email] \\
          Phone: phonenum
    \item \textbf{Dr.  Yang} \\
          Nuclear Physicist, John Hopkins Applied Physics Laboratory \\
          Email:  \\
          Phone: (240) 472-5225 
    \item \textbf{Commander n} \\
          Executive Officer, NOAA Commissioned Officer Corps \\
          Email:v \\
          Phone: (681) 443-0480
\end{itemize}}

\end{document}
